Advances in Artificial Intelligence for Data Visualization: Automated Reading of Residual Plots with Computer Vision

### 2023-04-18 Milestone_presentation_2/Milestone_presentation_2/Untitled.Rmd
finish effect size

>>>>

```{r}
magick::image_read_pdf("images/different-dist-1.pdf", pages = 1)
```

```{r out.width = "70%"}
magick::image_read_pdf("images/different-n-1.pdf", pages = 1)
```

.center[
.caption[
Fig. 5: _Four different distribution of fitted values that might affect perception of residual plots are used. Three differnet values of \\(n\\) are used to control the signal strength._
]
]

.center[
# 📏Effect size📏
]

We have chosen to use an approach based on **Kullback-Leibler divergence** (Kullback and Leibler 1951).

The effect size of the **non-linearity model** is

$$E = \frac{1}{2}\left(\boldsymbol{\mu}_z'(diag(\boldsymbol{R}\sigma^2))^{-1}\boldsymbol{\mu}_z\right),$$

where $diag(.)$ is the diagonal matrix constructed from the diagonal elements of a matrix,
$\boldsymbol{R} = \boldsymbol{I}_n - \boldsymbol{H}$ is the residual operator, $\boldsymbol{H} = \boldsymbol{X}(\boldsymbol{X}'\boldsymbol{X})^{-1}\boldsymbol{X}'$ is the hat matrix, $\boldsymbol{\mu}_z = \boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z$ is the expected values of residuals with $\boldsymbol{Z}$ be any higher order terms of $\boldsymbol{X}$ leave out by the regression equation and $\boldsymbol{\beta}_z$ be the corresponding coefficients, and $\sigma^2\boldsymbol{I}$ is the assumed covariance matrix of the error term when $H_0$ is true.

And the effect size of the **heteroskedasticity model** is

$$E = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|diag(\boldsymbol{R})|} - n + tr(diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}diag(\boldsymbol{R}))\right),$$
where $\boldsymbol{V}$ is the actual covariance matrix of the error term.
